
---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview
***

Binomial Package is a minimal R package that provides various calculations on binomial distribution.

Functions in this package include:

#### Summary functions
`summary()` computes summary of the binomial object
`bin_mean()` computes mean of binomial distribution
`bin_variance()` computes variance of a binomial distribution
`bin_mode()` computes mode of a binomial distribution
`bin_skewness()` computes skewness of a binomial distribution
`bin_kurtosis()` computes kurtosis(tailedness) of a binomial distribution

#### Main functions
`bin_choose()` computes number of combinations of successes
`bin_probability()` computes probability of successes
`bin_distribution()` computes binomial probability distribution
`bin_cumulative()` computes cumulative probabilities and binomial distribution
`bin_variable()` returns an object of class, binomial random variable object
`plot()` returns a barplot for bin_distribution and scatterplot with line for bin_cumulative

## Motivation
***
This package has been developed to illustrate some of the concepts behind the creation of an R package.

## Installation
***
Install the development version from GitHub via the package "devtools":

# development version from GitHub:
install.packages("devtools") 
```{r}
# development version from GitHub:
#install.packages("devtools")

# # install "binomial" (without vignettes)
# devtools::install_github("stat133-sp19/hw-stat133-jaesung29/tree/master/binomial")

# # install "binomial" (with vignettes)
# devtools::install_github("stat133-sp19/hw-stat133-jaesung29/tree/master/binomial", build_vignettes = TRUE)
```

## Usage
```{r}
library(binomial)

# mean or expected value of 10 trials and 0.3 probability of success
bin_mean(10, 0.5)

# variance of a binomial experiment with 10 trials and 0.3 probability of success
bin_variance(10, 0.5)

# mode(s) of a binomial experiment with 10 trials and 0.3 probability of success
bin_mode(10, 0.3)

# skewness of a binomial experiment with 10 trials and 0.3 probability of success
bin_skewness(10, 0.3)

# kurtosis of a binomial experiment with 10 trials and 0.3 probability of success
bin_kurtosis(10, 0.3)

# number of combinations of successes with 5 trials and 3 sucesses
bin_choose(5, 3)

# probability of successes with 3 sucesses, 5 trials and probability of success = 0.5
bin_probability(success = 5, trials = 5, prob = 0.5)

# binomial distribution with 5 trials and probability of success = 0.5
bin_distribution(trials = 5, prob = 0.5)

# binomial cumulative distribution with 5 trials and probability of success = 0.5
bin_cumulative(trials = 5, prob = 0.5)

# binomial random variable object with 5 trials and probability of success = 0.5
bin_variable(trials = 5, prob = 0.3)
```
