---
title: "Introduction"
author: "Jaesung Lee"
date: "05-03-2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")

library(binomial)
```

## Binomial distribution functions
The package provides various calculations on binomial distribution.

## bin_choose() computes the number of combinations in which k successes can occur in n trials
```{r}
bin_choose(n = 5, k = 3)
```

## bin_probability() computes the probability of getting the number of successes in trials with a probability of success on each trial
```{r}

```


# mean or expected value of 10 trials and 0.3 probability of success
bin_mean(10, 0.5)

# variance of a binomial experiment with 10 trials and 0.3 probability of success
bin_variance(10, 0.5)

# mode(s) of a binomial experiment with 10 trials and 0.3 probability of success
bin_mode(10, 0.3)

# skewness of a binomial experiment with 10 trials and 0.3 probability of success
bin_skewness(10, 0.3)

# kurtosis of a binomial experiment with 10 trials and 0.3 probability of success
bin_kurtosis(10, 0.3)

# number of combinations of successes with 5 trials and 3 sucesses
bin_choose(5, 3)

# probability of successes with 3 sucesses, 5 trials and probability of success = 0.5
bin_probability(success = 5, trials = 5, prob = 0.5)

# binomial distribution with 5 trials and probability of success = 0.5
bin_distribution(trials = 5, prob = 0.5)

# binomial cumulative distribution with 5 trials and probability of success = 0.5
bin_cumulative(trials = 5, prob = 0.5)

# binomial random variable object with 5 trials and probability of success = 0.5
bin_variable(trials = 5, prob = 0.3)
