---
title: "Introduction"
author: "Jaesung Lee"
date: "05-03-2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")

library(binomial)
```

## Binomial distribution functions
The package provides various calculations on binomial distribution.

## bin_choose() computes the number of combinations in which k successes can occur in n trials
```{r}
bin_choose(n = 5, k = 3)
```

## bin_probability() computes the probability of getting the number of successes on each trial
```{r}
bin_probability(success = 5, trials = 5, prob = 0.5)
```

## bin_distribution() computes the probability distribution for each outcome
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

## `plot()` is used to create a visual graphics for bin_distribution()
```{r}
plot(bin_distribution(trials = 5, prob = 0.5))
```

## bin_cumulative() is used to add cumulative probability in addition to the bin_distribution table
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

## `plot()` is used to create a visual graphics for bin_cumulative()
```{r}
plot(bin_cumulative(trials = 5, prob = 0.5))
```

## mean or expected value of the binomial distribution
```{r}
bin_mean(10, 0.2)
```

## vaiance of the binomial distribution
```{r}
bin_variance(10, 0.2)
```

## mode of the binomial distribution
```{r}
bin_mode(10, 0.2)
```

## skewness of the binomial distribution
```{r}
bin_skewness(10, 0.2)
```

## kurtosis of the binomial distribution
```{r}
bin_kurtosis(10, 0.2)
```

## summary of the binomial distribution
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```


